RickView: Lightweight Standalone Knowledge Graph Browsing

### 2024-03-22 paper.tex
add more stats

\begin{table}
\begin{tabular}{lSSSSSSS}
\toprule
% triples SNIK 44584, HITO, ANNO, linkedspending					
Knowledge Graph	&\textnormal{k triples}		&\textnormal{Size in MiB}	&\textnormal{LodView}	&\textnormal{Virtuoso}	&\textnormal{LodView+Virtuoso}	&\textnormal{RickView}\\
\midrule
SNIK v24.03		&44.6						&2.0						&						&127.8							&								&23.4\\
HITO v24.02		&							&1.0						&						&110.2							&								&18.2\\
ANNO			&							&\\
LinkedSpending	&							&28256.6					&						&								&								&1973.2\\
\bottomrule
\end{tabular}
\label{tab:stats}
% todo correct versions
\caption{Knowledge graph serialized size (uncompressed N-Triples) and total deployment RAM consumption of LodView 1.2.3, Virtuoso 7.2.12 and RickView 0.2.13 of SNIK v24.03, HITO v24.02, ANNO v00000 and LinkedSpending v2015.
LinkedSpending uses the compressed HDT mode, see \cref{sec:hdt}.
File sizes and memory usage in MiB rounded to one decimal place.}
\end{table}

@@

\subsection{RuThes}
\citep{ruthes}
Similar to LinkedSpending
Cyrillic URLs
The RuThes Cloud [RU], a linguistic resource for Russian, originally published with the LodView RDF browser but discontinued due to instability and high resource consumption, and revived by RV.

>>>>

\begin{table}
\begin{tabular}{lrrcSSSSS}
\toprule
% triples SNIK 44584, HITO, ANNO, linkedspending					
Knowledge Graph	&\textnormal{triples}		&\textnormal{N-Triples}	&\textnormal{HDT}	&\textnormal{LodView}	&\textnormal{Virtuoso}	&\textnormal{LodView+Virtuoso}	&\textnormal{RickView}\\
\midrule
SNIK	 		&45\,k~						&2.0\,MiB				& ---				&561					&207					&767							&23.4\\
HITO 			&14\,k~						&1.0\,MiB				& ---				&553					&121					&674								&18.2\\
ANNO			&30\,k~						&3.5\,MiB				& ---				&						&						&								&22.3\\
Ruthes			&15\,M						&3.7\,GiB				&146\,MiB			&						&						&								&203.4\\
LinkedSpending	&1350\,M					&28.2\,GiB				&1.4\,GiB			&						&						&								&1975.3\\
\bottomrule
\end{tabular}
\label{tab:stats}
% todo correct versions
\caption{Knowledge graph serialized size (uncompressed N-Triples) and total deployment RAM consumption of LodView 1.2.3, Virtuoso 7.2.12 and RickView 0.2.13 of SNIK v24.03, HITO v24.02, ANNO v24.02 and LinkedSpending v2015.
LinkedSpending uses the compressed HDT mode, see \cref{sec:hdt}.
%File sizes and memory usage in MiB rounded to one decimal place.
}
\end{table}

@@

\subsection{RuThes}
\citep{adaptinglodview}
Similar to LinkedSpending
Cyrillic URLs
The RuThes Cloud [RU], a linguistic resource for Russian, originally published with the LodView RDF browser but discontinued due to instability and high resource consumption, and revived by RV.
